# EWAS report
- study: `r study`
- author: `r author`
- date: `r format(Sys.time(), '%d %B, %Y')`

## Parameters

```{r, results="markup"}
ewas.summary$parameters
```

## Sample characteristics

For continuous or ordinal variables, the "mean" column provides the mean
and the "var" column the standard deviation of the variable.
For categorical variables, the "mean" column provides the number
of samples with the given "value" and the
"var" column the percentage of samples with the given "value".

```{r}
knitr::kable(ewas.summary$sample.characteristics)
```

## Covariate associations

```{r,include=FALSE}
if (!is.null(ewas.summary$covariate.associations)) {
    out <- NULL
    for (covariate.name in names(ewas.summary$covariate.associations))
        out <- c(out, knit_child(file.path(report.path, "ewas-covariate.rmd")))
}
```

```{r,results="asis"}
cat(out, sep="\n\n")
```

## QQ plots

```{r, include=FALSE}
out <- NULL
for (plot in ewas.summary$qq.plots)
    out <- c(out, knit_child(file.path(report.path, "qq-plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n")
```

## Manhattan plots

```{r, include=FALSE}
out <- NULL
for (plot in ewas.summary$manhattan.plots)
    out <- c(out, knit_child(file.path(report.path, "manhattan-plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n")
```

## Significant CpG sites

There were `r length(ewas.summary$significant.sites)`
CpG sites with association p-values < `r ewas.summary$parameters$sig.threshold`.
These are listed in the file [associations.csv](associations.csv).

```{r}
tab <- with(ewas.summary, cpg.stats[match(significant.sites, rownames(cpg.stats)),])
write.csv(tab, file=file.path(opts_knit$get("output.dir"), "associations.csv"))
```

The following table shows overlaps between
associations under different sets of covariates:
```{r}
p.value.idx <- grep("p.value", colnames(tab))
tab.overlaps <- apply(tab[,p.value.idx], 2, function(p.a) {
    apply(tab[,p.value.idx], 2, function(p.b) {
        sum(p.a < ewas.summary$parameters$sig.threshold
            & p.b < ewas.summary$parameters$sig.threshold, na.rm=T)
    })
})
knitr::kable(tab.overlaps)
```

```{r}
practical.sites <- setdiff(names(ewas.summary$cpg.plots),
                           ewas.summary$selected.sites)
tab <- with(ewas.summary, cpg.stats[match(practical.sites, rownames(cpg.stats)),])
```

Below are the `r length(practical.sites)`
CpG sites with association p-values < `r ewas.summary$parameters$practical.threshold`
in the `r ewas.summary$parameters$model` regression model.

```{r}
knitr::kable(tab[practical.sites,])
```

Plots of these sites follow, one for each covariate set.
"p[lm]" denotes the p-value obtained using a linear model
and "p[beta]" the p-value obtained using beta regression.

```{r, include=FALSE}
out <- NULL
for (cpg in practical.sites) 
    out <- c(out, knit_child(file.path(report.path, "cpg-plot.rmd")))
```

```{r}
cat(out, sep="\n")
```

## Selected CpG sites

Number of CpG sites selected: `r length(ewas.summary$selected.sites)`.

```{r}
tab <- with(ewas.summary, cpg.stats[match(selected.sites, rownames(cpg.stats)),])
knitr::kable(tab)
```

```{r, include=FALSE}
out <- NULL
for (cpg in ewas.summary$selected.sites)
    out <- c(out, knit_child(file.path(report.path, "cpg-plot.rmd")))
```

```{r}
cat(out, sep="\n\n")
```

## R session information

```{r, results="markup"}
sessionInfo()
```
