```{r qc-init, echo=FALSE}

library(knitr)
library(Cairo)
opts_chunk$set(warning=FALSE, echo=FALSE, message=FALSE, results="asis", fig.width=12, fig.height=12, dev="CairoPNG",error=FALSE)

```

# EWAS report
- study: `r study`
- author: `r author`
- date: `r format(Sys.time(), '%d %B, %Y')`

## Parameters

```{r ewas-parameters, results="markup"}
ewas.summary$parameters
```

## Sample characteristics

```{r sample-characteristics}
knitr::kable(ewas.summary$sample.characteristics)
```

## Covariate associations

```{r covariate-associations}
knitr::kable(ewas.summary$covariate.associations)
```

## QQ plots

```{r ewas-qq-plots, results="hide"}
for (p in ewas.summary$qq.plots) print(p)
```

## Manhattan plots

```{r ewas-manhattan-plots, results="hide"}
for (p in ewas.summary$manhattan.plots) print(p)
```

## Significant CpG sites

There were `r nrow(ewas.summary$sig.cpg.stats$p.value)`
CpG sites with association p-values < `r ewas.summary$parameters$sig.threshold`.
These are listed in the file [associations.csv](associations.csv).

```{r ewas-significant-sites}
tab <- cbind(ewas.summary$cpg.sites[rownames(ewas.summary$sig.cpg.stats$p.value),],
             p.value=ewas.summary$sig.cpg.stats$p.value,
             coefficient=ewas.summary$sig.cpg.stats$coefficient)
write.csv(tab, file=file.path(output.dir, "associations.csv"))
```

The following table shows overlaps between
associations under different sets of covariates:
```{r ewas-associations-overlap}
tab.overlaps <- apply(ewas.summary$sig.cpg.stats$p.value, 2, function(p.a) {
    apply(ewas.summary$sig.cpg.stats$p.value, 2, function(p.b) {
        sum(p.a < ewas.summary$parameters$sig.threshold
            & p.b < ewas.summary$parameters$sig.threshold, na.rm=T)
    })
})
knitr::kable(tab.overlaps)
```

```{r ewas-practical-sites}
practical.sites <- intersect(rownames(ewas.summary$sig.cpg.stats$p.value),
                             names(ewas.summary$cpg.plots))
```

Below are the `r length(practical.sites)`
CpG sites with association p-values < `r ewas.summary$parameters$practical.threshold`.

```{r ewas-practical-table}
knitr::kable(tab[practical.sites,])
```

```{r ewas-practical-plots, results="hide"}
for (cpg in practical.sites)
    print(do.call(grid.arrange, c(ewas.summary$cpg.plots[[cpg]], list(ncol=2))))
```

## Selected CpG sites

There were `r nrow(ewas.summary$sig.selected.stats$p.value)`
candidate CpG sites selected.
```{r ewas-selected-sites}
tab <- cbind(ewas.summary$cpg.sites[rownames(ewas.summary$selected.cpg.stats$p.value),],
             p.value=ewas.summary$selected.cpg.stats$p.value,
             coefficient=ewas.summary$selected.cpg.stats$coefficient)
knitr::kable(tab)
```

```{r ewas-selected-site-plots, results="hide"}
for (cpg in rownames(ewas.summary$selected.cpg.stats$p.value))
    print(do.call(grid.arrange, c(ewas.summary$cpg.plots[[cpg]], list(ncol=2))))
```

