There are
`r sum(!qc.summary$genotype.summary$tabs$samples$is.concordant)`
samples whose genotypes do not match the SNP probes on the microarray
(concordance threshold = `r qc.summary$parameters$sample.genotype.concordance.threshold`).

```{r genotype-discordant-samples}

tab <- qc.summary$genotype.summary$tabs$samples
tab <- tab[which(!tab$is.concordant),]
if (nrow(tab) > 0) kable(tab)

```

Sample concordances are distributed as follows:
```{r sample-genotype-graph}

qc.summary$genotype.summary$graphs$sample.concordance

```

There are
`r sum(!qc.summary$genotype.summary$tabs$snp$is.concordant)`
SNP probes whose genotypes do not match their values on the microarray
(concordance threshold = `r qc.summary$parameters$snp.concordance.threshold`).

```{r genotype-discordant-snps}

tab <- qc.summary$genotype.summary$tabs$snps
tab <- tab[which(!tab$is.concordant),]
if (nrow(tab) > 0) kable(tab)

```

SNP concordances are distributed as follows:

```{r snp-genotype-graph}

qc.summary$genotype.summary$graphs$snp.concordance

```
