There are
`r sum(!qc.summary$genotype.summary$tabs$samples$is.concordant, na.rm=T)`
samples whose genotypes do not match the SNP probes on the microarray
(concordance threshold = `r qc.summary$parameters$sample.genotype.concordance.threshold`).

```{r}

tab <- qc.summary$genotype.summary$tabs$samples
tab <- tab[which(!tab$is.concordant),]
if (nrow(tab) > 0) kable(tab,row.names=F)

```

Sample concordances are distributed as follows:
```{r,message=FALSE}

(qc.summary$genotype.summary$graphs$sample.concordance)

```

There are
`r sum(!qc.summary$genotype.summary$tabs$snp$is.concordant, na.rm=T)`
SNP probes whose genotypes do not match their values on the microarray
(concordance threshold = `r qc.summary$parameters$snp.concordance.threshold`).

```{r}

tab <- qc.summary$genotype.summary$tabs$snps
tab <- tab[which(!tab$is.concordant),]
if (nrow(tab) > 0) kable(tab,row.names=F)

```

SNP concordances are distributed as follows:

```{r,message=FALSE}

(qc.summary$genotype.summary$graphs$snp.concordance)

```
