
```{r echo=FALSE}

library(knitr)
library(meffil)
library(pander)
opts_chunk$set(warning=FALSE, echo=FALSE, message=FALSE, results="asis")
read_chunk(system.file("reports", "meffil.qc.report.r", package="meffil"))

```

```{r setup}

# sex.mismatch = sex
# bad.ids = removeids
# bad.cpgs = removecpgs
# parameters = parameters
# sex.summary = sex.summary
# meth.unmeth.summary = meth.unmeth.summary
# controlmeans.summary = controlmeans.summary
# sample.detectionp.summary = sample.detectionp.summary
# cpg.detectionp.summary = cpg.detectionp.summary
# sample.beadnum.summary = sample.beadnum.summary
# cpg.beadnum.summary = cpg.beadnum.summary

load(file.path(tempdir(), "meffil.qc.report.rdata"))

```

---
title: QC report for "`r studyname`"
author: "`r author`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

* * *


## Parameters used for QC

```{r }

pander(qc.summary$parameters)

```


## Sex mismatches

There are `r sum(qc.summary$sex.summary$tab$outliers)` sex detection outliers, and `r sum(qc.summary$sex.summary$tab$sex.mismatch)` sex detection mismatches.

```{r }

tab <- qc.summary$sex.check
if(nrow(tab) > 0) pander(tab)

```

This is a plot of the `xy.diff` values estimated from the methylation data.

```{r }

qc.summary$sex.summary$graph

```


## Methylated vs unmethylated

There are `r sum(qc.summary$meth.unmeth.summary$tab$outliers)` outliers from the meth vs unmeth comparison.

```{r }

tab <- subset(qc.summary$meth.unmeth.summary$tab, outliers)
if(nrow(tab) > 0) pander(tab)

```

This is a plot of the methylation signals vs unmethylated signals

```{r }

qc.summary$meth.unmeth.summary$graph

```


## Control probe means

There were `r sum(qc.summary$controlmeans.summary$tab$outliers)` outliers detected based on deviations from mean values for control probes.

```{r }

tab <- subset(qc.summary$controlmeans.summary$tab, outliers)
if(nrow(tab) > 0) pander(tab)

```

The distribution of sample control means are plotted here:

```{r }

qc.summary$controlmeans.summary$graph

```


## Sample detection p-values

There were `r sum(qc.summary$sample.detectionp.summary$tab$outliers)` outliers detected based on having low detection p-values

```{r }

tab <- subset(qc.summary$sample.detectionp.summary$tab, outliers)
if(nrow(tab) > 0) pander(tab)

```

Distribution:

```{r }

qc.summary$sample.detectionp.summary$graph

```


## Sample bead numbers

There were `r sum(qc.summary$sample.beadnum.summary$tab$outliers)` outliers detected based on having low average bead numbers

```{r }

tab <- subset(qc.summary$sample.beadnum.summary$tab, outliers)
if(nrow(tab) > 0) pander(tab)

```

Distribution:

```{r }

qc.summary$sample.beadnum.summary$graph

```


## CpG detection p-values

There were `r sum(qc.summary$cpg.detectionp.summary$tab$outliers)` CpGs with low detection p-values.

```{r }

tab <- subset(qc.summary$cpg.detectionp.summary$tab, outliers)
if(nrow(tab) > 0) pander(tab)

```

Manhattan plot of detection p-values for CpGs:

```{r }

qc.summary$cpg.detectionp.summary$graph

```

## CpG low bead numbers

There were `r sum(qc.summary$cpg.beadnum.summary$tab$outliers)` CpGs with low bead numbers.

```{r }

tab <- subset(qc.summary$cpg.beadnum.summary$tab, outliers)
if(nrow(tab) > 0) pander(tab)

```

Manhattan plot of detection p-values for CpGs:

```{r }

qc.summary$cpg.beadnum.summary$graph

```
