# Normalization performance report
- study: `r study`
- author: `r author`
- date: `r format(Sys.time(), '%d %B, %Y')`

## Parameters used to test normalization

```{r, results="markup"}

normalization.summary$parameters

```

## Control probe scree plots

The variance captured by each principal component.

```{r,include=FALSE,message=F}
out <- NULL
for (plot in normalization.summary$scree.plot$graphs)
    out <- c(out, knit_child(file.path(report.path, "plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n\n")
```

## Principal components of the control probes

The following plots show the first 3 principal components of the
control matrix colored by batch variables.
Batch variables with more than 10 levels are omitted.

```{r,include=FALSE,message=F}
out <- NULL
for (plot in normalization.summary$control.batch$pc.plots)
    out <- c(out, knit_child(file.path(report.path, "wide-plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n\n")
```

## Control probe associations with measured batch variables

Principal components of the control probes were regressed against batch variables.
Shown are the $-log_{10}$ p-values for these regressions.
The horizontal dotted line denotes $p = 0.05$ in log-scale.

```{r,include=FALSE,message=F}
out <- NULL
for (plot in normalization.summary$control.batch$fplots)
    out <- c(out, knit_child(file.path(report.path, "wide-plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n\n")
```


The following plots show regression coefficients when
each principal component is regressed against each batch variable level
along with 95% confidence intervals.
Cases significantly different from zero are coloured red
(p < `r normalization.summary$parameters$batch.threshold`, t-test).

```{r,include=FALSE,message=F}
out <- NULL
for (plot in normalization.summary$control.batch$cplots)
    out <- c(out, knit_child(file.path(report.path, "plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n\n")
```

```{r}

tab <- normalization.summary$control.batch$tab
tab <- tab[which(tab$p.value < normalization.summary$parameters$batch.threshold),]
for (i in 1:ncol(tab)) {
    if (is.numeric(tab[,i])) {
        tab[,i] <- format(tab[,i], digits=3)
        tab[,i] <- sub("^[ ]*NA$", "", tab[,i])
    }
    if (any(is.na(tab[,i])))
        tab[which(is.na(tab[,i])),i] <- ""
}
if(nrow(tab) > 0) kable(tab,row.names=F)

```

## Principal components of the normalized betas

The following plots show the first 3 principal components of the
`r normalization.summary$parameters$probe.range` most variable
probes colored by batch variables.
Batch variables with more than 10 levels are omitted.

```{r,include=FALSE,message=F}
out <- NULL
for (plot in normalization.summary$probe.batch$pc.plots)
    out <- c(out, knit_child(file.path(report.path, "wide-plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n\n")
```

## Normalized probe associations with measured batch variables

The most variable normalized probes were extracted, decomposed into
principal components and each component regressed against each batch
variable. If the normalization has performed well then there will be
no associations between normalized probe PCs and batch
variables. Horizontal dotted line denotes $p = 0.05$ in log-scale.

```{r,include=FALSE,message=F}
out <- NULL
for (plot in normalization.summary$probe.batch$fplots)
    out <- c(out, knit_child(file.path(report.path, "wide-plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n\n")
```

The following plots show regression coefficients when
each principal component is regressed against each batch variable level
along with 95% confidence intervals.
Cases significantly different from zero are coloured red
(p < `r normalization.summary$parameters$batch.threshold`, t-test).

```{r,include=FALSE,message=F}
out <- NULL
for (plot in normalization.summary$probe.batch$cplots)
    out <- c(out, knit_child(file.path(report.path, "plot.rmd")))
```

```{r,results="asis"}
cat(out, sep="\n\n")
```

```{r}

tab <- normalization.summary$probe.batch$tab
tab <- tab[which(tab$p.value < normalization.summary$parameters$batch.threshold),]
for (i in 1:ncol(tab)) {
    if (is.numeric(tab[,i])) {
        tab[,i] <- format(tab[,i], digits=3)
        tab[,i] <- sub("^[ ]*NA$", "", tab[,i])
    }
    if (any(is.na(tab[,i])))
        tab[which(is.na(tab[,i])),i] <- ""
}
if(nrow(tab) > 0) kable(tab,row.names=F)

```
